Response to reviewers

### 2025-01-23 Manuscript/supplementaries.tex
Update supplementaries.tex

\begin{figure}[!htbp]
\centering
   \includegraphics{Figures/empirical_data_dimensions.pdf}
\caption{\scriptsize{\textbf{Selection of the number of dimensions for the empirical data:} each histograms corresponds to the variance per dimension (dark grey) and the cumulative variance per dimension (light grey) for each group in the empirical data: the 37 currently endemic Hawaiian species (extant species) the 63 species present before 1500 (pre-1500 group). The plot shows that although 4 dimensions are enough to describe at least 95\% of the variance for the extant group, 5 dimensions are required for the pre-1500 group (following the method proposed in \cite{guillerme2023innovation}).
}}
\label{Fig:empirical_dimensions}
\end{figure}
\bigskip

>>>>

\begin{figure}[!htbp]
\centering
   \includegraphics{Figures/empirical_data_dimensions.pdf}
\caption{\scriptsize{\textbf{Selection of the number of dimensions for the empirical data:} each histograms corresponds to the variance per dimension (dark grey) and the cumulative variance per dimension (light grey) for each group in the empirical data: the 37 currently endemic Hawaiian species (extant species) the 63 species present at 1500 (``at 1500'' group). The plot shows that although 4 dimensions are enough to describe at least 95\% of the variance for the extant group, 5 dimensions are required for the ``at 1500'' group (following the method proposed in \cite{guillerme2023innovation}).Note that the whole trait space (light grey) contains 118 species. The 18 species extinct before 1500 are not contained in either of these groups.}}
\label{Fig:empirical_dimensions}
\end{figure}
\bigskip
